Precise Weed and Maize Classification through Convolutional Neuronal Networks

### 2017-08-25 PaperBCJ.tex
Final Student Revision
Revision

@@

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{C\'ordova-Cruzatty Andrea \IEEEauthorrefmark{1},
Barreno Barreno Mauricio Daniel \IEEEauthorrefmark{2} and J\'acome Barrionuevo Jos\'e Misael \IEEEauthorrefmark{3}}
\IEEEauthorblockA{Department of Energy and Mechanics,
University of the Armed Forces ESPE\\
Latacunga - Quijano y Ordo\~nez and Hermanas Pa\'ez \\
Email: \IEEEauthorrefmark{1}accordova@espe.edu.ec,
\IEEEauthorrefmark{2}mdbarreno@espe.edu.ec,
\IEEEauthorrefmark{3}jmjacome1@espe.edu.ec}}
% conference papers do not typically use \thanks and this command
% is locked out in conference mode. If really needed, such as for
% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
% after \documentclass

@@

Deep Learning is playing an important role in big data processing for more accurate modeling of common productive processes. It is being widely used in artificial vision applications and specifically in pattern recognition. The versatility of deep learning has positioned it as a fit tool used in many fields of application, among which is precision agriculture. This paper presents the development of an algorithm capable of image segmentation and classification. Segmentation is intended to separate the target plant from the original image, while classification is meant to identify what images belong to the two defined classes. It applies a convolutional neural network (CNN) to discriminate maize plants from weeds in real time, at early crop development stages. It was applied to maize crop because it is a common staple crop in the Ecuadorian Highlands.  The convolutional neural network has been trained with a dataset generated in the segmentation stage. The performance of the network was analyzed with LeNET, AlexNet, cNET and sNET network architectures. The network architecture that presented the best training results was cNET based on its performance in terms of accuracy (96.4\%) and processing time of 161 miliseconds in a Raspberry Pi CPU. The minimum working filter number for this network architecture was 16. The best performing algorithms and processors have a significant potential for autonomous weed and crop classification systems in a real-time application.\\

@@

\section{Introduction}
During the last centuries, significant progress has taken place in science and technology developments. Significant milestones in diverse areas such as communications, numerical computer control and the miniaturization of components have benefited industrial and productive sectors \cite{davim2017microfabrication}, providing new means to approach problems in a different manner. The availability of leading edge technologies has considerably increased, thus becoming more accessible to people. This effect of globalization has allowed many countries to have access to state-of-the-art technological products\cite{grossman2015globalization}, promoting its application in different areas to generate alternative and more efficient solutions to conventional problems. 
\\

@@

Weed and crop segmentation is not limited to color images. In another application \cite{potena2016fast}, the use of a a multispectral camera permitted to obtain RGB and NIR images for the segmentation and classification purposes. The images used a light CNN for the first process and a deep CNN for classification, its accuracy was as high as 98\% in the identification of weeds. One of the most difficult things in crop identification is the generation of datasets due to weed presence in the training images, but these can be correctly generated by the use of a CNN \cite{di2016automatic}, achieving an acceptable accuracy for the generation of datasets. \\
\section{Matherials and Methods}
\begin{comment}
El desarrollo del modelo para la identificacion de mala hierba y maiz usando Redes Neuronales Convoluciones se describe abajo: 
\end{comment}
The developed model for weed and maize identification algorithm using convolutional neural networks is described below.
\subsection{Hardware}
\begin{comment}
Para la etapa de entranamiento y captura de imagenes, los siguientes elementos fueron utilizados: Una Raspberry Pi 3 con su modulo de camara V2.1 para la adquisicion de imagenes, fue configurado para obtener video en resolucion de 1280x720 pixeles con el fin de obtener mayor detalle en la segmentacion de imagenes. Debido a la popularidad de la computacion por GPU(IDEA COMPLETADA) por sus ventajas en el desarrollo de modelos de Redes Neuronales Convolucionales, fue necesario consider hardware compatible con computacion paralela como las tarjetas graficas fabricadas por NVIDIA, estas tienen la ventaja de poseer mejores tiempos de procesamiento comparados con la CPU, con lo cual se logra optimizar los tiempos de clasificacion y entrenamiento de Modelos de Deep Learning, entonces, utilizamos un computador con una tarjeta Grafica NVIDIA GTX950M. Tambien fue necesario considerar el uso de un CPU Core i7 2.7Ghz, 8 Nucles and el CPU de la propia Raspberry Pi 3, un ARM 3, a ARM Cortex-A53, 1.2GHz, 4 nucles para probar el rendimiento de red en un sistema portable para su aplicacion en un sistema movil independiente . El hardware escogido sera probado para clasificar las imagenes y medir los tiempos de clasificacion para su posterior analisis. El hardware elegido será probado para clasificar imágenes, en cada clasificación se medirán los tiempos de procesamiento, para realizar un análisis si el hardware puede procesar en tiempo real 
\end{comment}

A Raspberry Pi 3 with a V2.1 Pi camera for image acquisition was used for the training and image-capturing stages. The system was configured to obtain a video at a resolution of 1280x720 pixels in order to get more detail in the segmented images. Due to the popularity of GPU computing for its advantages in the development of models of Convolutional Neural Networks, such as a better processing speed, it was necessary to consider hardware compatible with parallel computing devices such as the Graphic Cards manufactured by NVIDIA. These cards have the advantage of a superior processing speed compared to a CPU in order to optimize image-processing time and deep learning Model's training process, thus the selected device was a computer with a Nvidia graphics card GTX950M. Also, it was necessary to consider the use of a Core i7 2.7 Ghz CPU of 8 cores and the CPU of the Raspberry Pi 3, with an ARM Cortex-A53, 1.2GHz, and 4 cores, in order to test their performance for a future application in an independent mobile system that could be implemented in an embedded system. The hardware chosen will be tested to classify images, in each classification a measurement of the processing time will be taken to analyze if the hardware can process information in real time. 
\\

@@

Then, through a first-stage digital image processing procedure, the images were normalized in its green channel. This was done in order to improve green color detection based on the elimination of light and shadow in the images. Later, the green color was extracted from the images to obtain a grayscale equivalent; this was done through   (\ref{eqn:1}) described by Wang, Meng, Luo and Mei \cite{wang2013path}. Following, an OTSU Thresholding was applied to the grayscale images in order to obtain a binary mask. 
\begin{equation}
\label{eqn:1}
	S = 2*G - R - B
\end{equation}

@@

Once image processing was completed, a set of 2835 maize images and 880 weed images was obtained. Lee \textit{et. al} \cite{lee2015deep} said that once CNN has reached an acceptable accuracy, the dataset can be extended by means of geometric transformations. In addition, geometric transformations \cite{sladojevic2016deep} allow overfitting reduction and improve precision in the training process. For this reason, the obtained images were rotated every 30 degrees, obtaining an increment of the dataset by 12 times, thus increasing the chances of effectively recognizing plants that are in any orientation. \\

@@

For the validation phase, a fifth part of the total image set of each class was chosen, resulting in the dataset distribution shown in Table \ref{table:1}.

@@

One of the characteristics of CNN is these have multiple architectures, each architecture can reach different results depending on the application. For the present document four CNN architectures have been considered. Two arquitectures were chosen from the Caffe Zoo Model(a free resource provided by Caffe Developers), LeNet and AlexNet. Also, Potena and Nardi\cite{potena2016fast} used two additional types of architectures, sNET and cNET, which sucessfully proved an aceptable performance in plants and crop identification processes. With the four Nets chosen, each one was trained with the same solver of type Adam and with the same dataset. The training results are shown in Table \ref{table:2}. \\
\begin{table}[h!]
\centering
\renewcommand{\arraystretch}{1.2}
\caption{Comparison of the 4 types of CNN}
\label{table:2}
\begin{tabular}{|l c c c c|} 
 \hline
 \textbf{Parameters }& \textbf{LeNet} & \textbf{AlexNet} & \textbf{cNET} & \textbf{sNET} \\ [0.75ex] 
 \hline
 Input size of images & 32x32 & 64x64 & 64x64 & 64x64 \\ 
 Layers numbers & 9 & 11 & 8 & 4\\
 Number of parameters & 652500 & 20166688 & 6421568 & 135872 \\ 
 Iterations & 3000 & 3000 & 3000 & 3000 \\ 
 Accuracy(\%) & 86.48 & 93.86 & 96.4 & 80.4 \\
 Loss(\%) & 32.80 & 15.32 & 13.72 & 15.32 \\ [1ex] 
 \hline 
\end{tabular}
\end{table}

@@

\begin{table}[h!]
\centering
\renewcommand{\arraystretch}{1.2}
\caption{Test of complete image classification in FPS}
\label{table:6}
\begin{tabular}[c c c c]{|p{1.1 cm} p{1.7cm} p{1.7cm} p{2.0cm}|} 
 \hline
 \textbf{Parameter} &\textbf{GPU(Without Threading) } & \textbf{CPU with Threading} & \textbf{Raspberry Pi 3 with Threading} \\ 
 \hline
 Time(s) & 0.0171 & 0.196 & 2.714 \\ [0.95ex]
 FPS & 58.47 & 5.08 & 0.36 \\ [0.95ex]
 \hline
\end{tabular}
\end{table}

@@

In order to have adequate image processing that could be implemented to work in real time, the number of network filter layers was reduced from 64 to 16, reducing the number of parameters to be computed during the classification. A classification time reduced by 2.5 times compared the original Net of 64 filters was obtained. This change had a small impact in the training accuracy of the net, its value increased 1 \% in comparison to the original net. \\

@@

The study demonstrated that performimg geometrical transformations to the dataset images improves plant classification accuracy since the plants will have different orientations in the crop field. \\

@@

This work has been supported by the University of the Army "ESPE" Latacunga.

>>>>

\usepackage{makecell}

@@

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{C\'ordova-Cruzatty Andrea \IEEEauthorrefmark{1},
Barreno Barreno Mauricio Daniel \IEEEauthorrefmark{2} and J\'acome Barrionuevo Jos\'e Misael \IEEEauthorrefmark{3}}
\IEEEauthorblockA{Departamento de Energ\'ia y Mec\'anica,
Universidad de las Fuerzas Armadas  ESPE\\
Sangolqu\'i - Ecuador \\
Email: \IEEEauthorrefmark{1}accordova@espe.edu.ec,
\IEEEauthorrefmark{2}mdbarreno@espe.edu.ec,
\IEEEauthorrefmark{3}jmjacome1@espe.edu.ec}}
% conference papers do not typically use \thanks and this command
% is locked out in conference mode. If really needed, such as for
% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
% after \documentclass

@@

Deep Learning is playing an important role in big data processing for more accurate modeling of common productive processes. It is being widely used in artificial vision applications and specifically in pattern recognition. The versatility of deep learning has positioned it as a fit tool used in many fields of application, among which is precision agriculture. This paper presents the development of an algorithm capable of image segmentation and classification. Segmentation is intended to separate the target plant from the original image, while classification is meant to identify what images belong to the two defined classes. It applies a convolutional neural network (CNN) to discriminate maize plants from weeds in real time, at early crop development stages. It was applied to maize crop because it is a common staple crop in the Ecuadorian Highlands.  The convolutional neural network has been trained with a dataset generated in the segmentation stage. The performance of the network was analyzed with LeNET, AlexNet, cNET and sNET network architectures. The network architecture that presented the best training results was cNET based on its performance in terms of accuracy and processing time. The minimum working filter number for this network architecture was 16. The best performing algorithms and processors have a significant potential for autonomous weed and crop classification systems in a real-time application.\\

@@

\section{Introduction}
During the last centuries, significant progress has taken place in science and technology developments. Significant milestones in diverse areas such as communications, numerical computer control and the miniaturization of components have benefited industrial and productive sectors \cite{davim2017microfabrication}, providing new means to approach problems in a different manner. The availability of leading edge technologies has considerably increased, thus becoming more accessible to people. This effect of globalization has allowed many countries to have access to state-of-the-art technological products \cite{grossman2015globalization}, promoting its application in different areas to generate alternative and more efficient solutions to conventional problems. 
\\

@@

Weed and crop segmentation is not limited to color images. In another application \cite{potena2016fast}, the use of a multispectral camera permitted to obtain RGB and NIR images for the segmentation and classification purposes. The images used a light CNN for the first process and a deep CNN for classification, its accuracy was as high as 98\% in the identification of weeds. One of the most difficult things in crop identification is the generation of datasets due to weed presence in the training images, but these can be correctly generated by the use of a CNN \cite{di2016automatic}, achieving an acceptable accuracy for the generation of datasets. \\
\section{Matherials and Methods}
\begin{comment}
El desarrollo del modelo para la identificacion de mala hierba y maiz usando Redes Neuronales Convoluciones se describe abajo: 
\end{comment}
The developed model for weed and maize identification algorithm using convolutional neural networks is described below.
\subsection{Hardware}
\begin{comment}
Para la etapa de entranamiento y captura de imagenes, los siguientes elementos fueron utilizados: Una Raspberry Pi 3 con su modulo de camara V2.1 para la adquisicion de imagenes, fue configurado para obtener video en resolucion de 1280x720 pixeles con el fin de obtener mayor detalle en la segmentacion de imagenes. Debido a la popularidad de la computacion por GPU(IDEA COMPLETADA) por sus ventajas en el desarrollo de modelos de Redes Neuronales Convolucionales, fue necesario consider hardware compatible con computacion paralela como las tarjetas graficas fabricadas por NVIDIA, estas tienen la ventaja de poseer mejores tiempos de procesamiento comparados con la CPU, con lo cual se logra optimizar los tiempos de clasificacion y entrenamiento de Modelos de Deep Learning, entonces, utilizamos un computador con una tarjeta Grafica NVIDIA GTX950M. Tambien fue necesario considerar el uso de un CPU Core i7 2.7GHz, 8 Nucles and el CPU de la propia Raspberry Pi 3, un ARM 3, a ARM Cortex-A53, 1.2GHz, 4 nucles para probar el rendimiento de red en un sistema portable para su aplicacion en un sistema movil independiente . El hardware escogido sera probado para clasificar las imagenes y medir los tiempos de clasificacion para su posterior analisis. El hardware elegido será probado para clasificar imágenes, en cada clasificación se medirán los tiempos de procesamiento, para realizar un análisis si el hardware puede procesar en tiempo real 
\end{comment}

A Raspberry Pi 3 with a V2.1 Pi camera for image acquisition was used for the training and image-capturing stages. The system was configured to obtain a video at a resolution of 1280x720 pixels in order to get more detail in the segmented images. Due to the popularity of GPU computing for its advantages in the development of models of Convolutional Neural Networks, such as a better processing speed, it was necessary to consider hardware compatible with parallel computing devices such as the Graphic Cards manufactured by NVIDIA. These cards have the advantage of a superior processing speed compared to a CPU in order to optimize image-processing time and deep learning Model's training process, thus the selected device was a computer with a Nvidia graphics card GTX950M. Also, it was necessary to consider the use of a Core i7 2.7 GHz CPU of 8 cores and the CPU of the Raspberry Pi 3, with an ARM Cortex-A53, 1.2 GHz, and 4 cores, in order to test their performance for a future application in an independent mobile system that could be implemented in an embedded system. The hardware chosen will be tested to classify images, in each classification a measurement of the processing time will be taken to analyze if the hardware can process information in real time. 
\\

@@

Then, through a first-stage digital image processing, the images were normalized in its green channel. This was done in order to improve green color detection based on the elimination of light and shadow in the images. Later, the green color was extracted from the images to obtain a grayscale equivalent; this was done through   (\ref{eqn:1}) described by Wang, Meng, Luo and Mei \cite{wang2013path}. Following, an OTSU Thresholding was applied to the grayscale images in order to obtain a binary mask. 
\begin{equation}
\label{eqn:1}
	S = 2*G - R - B
\end{equation}

@@

Once image processing was completed, a set of 2835 maize images and 880 weed images was obtained. Lee \textit{et. al} \cite{lee2015deep} said that once CNN has reached an acceptable accuracy, the dataset can be extended by applying geometric transformations. In addition, geometric transformations  \cite{sladojevic2016deep} allow overfitting reduction and improve precision in the training process. For this reason, the obtained images were rotated every 30 degrees, obtaining an increment of the dataset by 12 times, thus increasing the chances of effectively recognizing plants that are in any orientation. \\

@@

For the validation phase, randomly the fifth part of the total image set of each class was chosen, resulting in the dataset distribution shown in Table \ref{table:1}.

@@

One of the characteristics of CNN is these have multiple architectures, each architecture can reach different results depending on the application. For the present document four CNN architectures have been considered. Two arquitectures were chosen from the Caffe Zoo Model(a free resource provided by Caffe Developers), LeNet and AlexNet. Also, Potena and Nardi  \cite{potena2016fast} used two additional types of architectures, sNET and cNET, which sucessfully proved an aceptable performance in plants and crop identification processes. With the four Nets chosen, each one was trained with the same solver of type Adam and with the same dataset. The training results are shown in Table \ref{table:2}. \\
\begin{table}[h!]
\centering
\renewcommand{\arraystretch}{1.2}
\caption{Comparison of the 4 types of CNN}
\label{table:2}
\begin{tabular}{|l c c c c|} 
 \hline
 \textbf{Parameters }& \textbf{LeNet} & \textbf{AlexNet} & \textbf{cNET} & \textbf{sNET} \\ [0.75ex] 
 \hline
 Input size of images & 32x32 & 64x64 & 64x64 & 64x64 \\ 
 Layers numbers & 9 & 11 & 8 & 4\\
 Number of parameters & 652500 & 20166688 & 6421568 & 135872 \\ 
 Iterations & 3000 & 3000 & 3000 & 3000 \\ 
 Accuracy(\%) & 86.48 & 93.86 & 96.4 & 80.4 \\
 Loss(\%) & 32.80 & 15.32 & 13.72 & 15.32 \\ [1ex] 
 \hline 
\end{tabular}
\end{table}

@@

\begin{table}[h!]
\centering
\renewcommand{\arraystretch}{1.2}
\caption{Test of complete image classification in FPS}
\label{table:6}
\begin{tabular}[c c c c]{|p{1.0 cm} p{1.7cm} p{1.7cm} p{1.7cm}|} 
 \hline
 \textbf{Parameter} &\textbf{GPU(Without Threading) } & \textbf{CPU (Threading)} & \textbf{Raspberry Pi (Threading)} \\ 
 \hline
 Time(s) & 0.0171 & 0.196 & 2.714 \\ [0.95ex]
 FPS & 58.47 & 5.08 & 0.36 \\ [0.95ex]
 \hline
\end{tabular}
\end{table}

@@

In order to have an adequate image processing that could be implemented to work in real time, the number of network filter layers was reduced from 64 to 16, reducing the number of parameters to be computed during the classification. A classification time reduced by 2.5 times compared the original Net of 64 filters was obtained. This change had a small impact in the training accuracy of the net, its value increased 1 \% in comparison to the original net. \\

@@

The study demonstrated that performing geometrical transformations to the dataset images improves plant classification accuracy since the plants will have different orientations in the crop field. \\

@@

This work has been supported by the Universidad de las Fuerzas Armadas ESPE.
